Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-01-07 manuscript/tables&figures.Rmd
worked on Table 1/ hypotheses
#67

```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/table1_hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "**Table 1. Summary of hypotheses, corresponding specific predictions, and results.** We count predictions as fully supported / rejected when the response matches/contradicts the prediction in both univariate and all top multivariate models (when applicable). Parentheses indicate that predictions were partially supported/ rejected--i.e., that the direction of response matched/contradicted the prediction but that the effect was not significant in all models.") %>%
  pack_rows("H1.0. Larger-diameter trees have lower drought resistance (Rt).", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.1. Tall trees have lower drought resistance.", 2, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.2. Trees with more exposed crowns have lower drought resistance.", 3, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.3. Small trees (lower root volume) suffer more in drier microhabitats.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H2.1. Species traits predict drought resistance.", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1cm") %>%
  column_spec(6, width = "2.4cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5) %>%
  kableExtra::landscape()
```
\clearpage

 ```{r Table 2, eval = TRUE, echo=FALSE, warning=FALSE}
  library(knitr)
  library(kableExtra)
  table2 <- read.csv("tables_figures/table2_variables_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
  kable(table2, booktabs = TRUE, caption = "**Table 2. Summary of variables**") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 10, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," "," ", "observed values" = 3, " ")) %>%
  column_spec(4, width = "7cm") %>%
  pack_rows("Dependent variable", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Independent variables", 2, 18, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("tree size", 5, 6, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("microhabitat", 7, 11, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("species' traits", 12, 17, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  kable_styling()
```
\clearpage

>>>>

```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/table1_hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "**Table 1. Summary of hypotheses, corresponding specific predictions, and results.** We count predictions as fully supported / rejected when the response matches/contradicts the prediction in both univariate and all top multivariate models (when applicable). Parentheses indicate that predictions were partially supported/ rejected--i.e., that the direction of response matched/contradicted the prediction but that the effect was not significant in all models.") %>%
  pack_rows("Tree size and microenvironment", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1a. Larger, taller trees have lower drought resistance (Rt).", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1b. Trees with more exposed crowns have lower drought resistance.", 3, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1c. Small trees (lower root volume) suffer more in drier microhabitats.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species traits", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H2a. conventional traits....", 6, 7, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H2b. leaf hydraulic traits....", 9, 10, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1cm") %>%
  column_spec(6, width = "2.4cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5) %>%
  kableExtra::landscape()
```
\clearpage

 ```{r Table 2, eval = TRUE, echo=FALSE, warning=FALSE}
  library(knitr)
  library(kableExtra)
  table2 <- read.csv("tables_figures/table2_variables_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
  kable(table2, booktabs = TRUE, caption = "**Table 2. Summary of variables**") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 10, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," "," ", "observed values" = 3, " ")) %>%
  column_spec(4, width = "7cm") %>%
  pack_rows("Dependent variable", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Independent variables", 2, 18, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("tree size", 5, 6, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("microhabitat", 7, 11, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("species' traits", 12, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  kable_styling()
```
\clearpage
